---
categories:
- ""
- ""
date: "2017-10-31T22:26:13-05:00"
description: "My CV"
draft: false
image: ""
keywords: ""
slug: blog3
title: "My CV"
---



```{r, setup, echo=FALSE}
knitr::opts_chunk$set(
  message = FALSE, 
  warning = FALSE, 
  tidy=FALSE,     # display code as typed
  size="small")   # slightly smaller font for code
options(digits = 3)

# default figure size
knitr::opts_chunk$set(
  fig.width=6.75, 
  fig.height=6.75,
  fig.align = "center"
)
```



```{r load-libraries, echo=FALSE}
library(tidyverse)  # Load ggplot2, dplyr, and all the other tidyverse packages
library(mosaic)
library(ggthemes)
library(lubridate)
library(here)
library(skimr)
library(janitor)
library(httr)
library(readxl)
library(vroom)
library(tidyquant)
library(tidytext)
library(scales)
```



# Paul Behrends

![](https://media-exp1.licdn.com/dms/image/C4D03AQHBogYjD5TgNQ/profile-displayphoto-shrink_200_200/0?e=1603324800&v=beta&t=7mKsZIVg4OVuJhLoQuyqHlbenVRN9qyCaCTr5P2NFxc)

* My name is Paul, I'm German and I was born on _February 15th, 1997_
* [Linkedin](https://www.linkedin.com/in/p-behrends/)

## Education
* _2020-2022_ **London Business School** (Masters in Financial Analysis)
*  _2015-2019_ **Bocconi University** (Bachelor in Economics and Management)

## Work Experience
* _2020-2020 (3 months)_ **Rothschild & Co** (Intern in Frankfurt Office)
* _2019-2019 (3 months)_ **DZ Bank** (Intern in Frankfurt Office)
* _2019-2019 (3 months)_ **goetzpartners Consultants** (Intern in Munich Office)
